Collective behavior of Suspended Janus Particles via an Integral Equation Method

### 2022-05-13 doc/PRF2022/PRF_main.tex
update

\begin{align}
  \label{eq:velocity}
  \uu(\xx) = \uu_\infty(\xx) + \DD[\eeta](\xx) + 
    \sum_{i=1}^{N_b} \left(\SS(\xx,\aa_i) \cdot \FF_i + 
    \RR(\xx,\aa_i) T_i\right), \quad \xx \in \Omega.
\end{align}
%
where the density function $\eeta$, translation velocity $\vv_i$ and angular velocity $\omega_i$ satisfy

@@

>>>>

\begin{align}
  \label{eq:velocity}
  \uu(\xx) = \uu_\infty(\xx) + \DD[\eeta](\xx) + 
    \sum_{i=1}^{N_b} \left(\SS(\xx,\aa_i) \cdot \FF_i + 
    \RR(\xx,\aa_i) T_i\right), \quad \xx \in \Omega.
\end{align}
%
where the number of particles $N_b$, the density function $\eeta$, translation velocity $\vv_i$ and angular velocity $\omega_i$ satisfy

@@

Figure~\ref{fig:relax_energy} shows the energy profile of boundary conditions (i)--(iii) using 
\eqref{eq:free_energy2} with \eqref{eq:normal_deriv} for normal derivative expression. As expected, for all simulation runs, the total energy of the systems decreases and reaches equilibrium states.
